A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-11 02_filtering_data.Rmd
take care to not eval

```{r}
fwrite(data_copy, file = "data/data_errors.csv")
```

@@

```{r}
# get 90 and 95 percentile of speed and turning angle
sapply(data_copy[, c("in_speed", "angle")], function(z) {
  quantile(z, probs = c(0.9, 0.95), na.rm = TRUE)
})
```

@@

```{r}
# filter the copy by the 95th percentile
data_filtered <- atl_filter_covariates(data_copy,
    filters = c("(in_speed < 0.024 & out_speed < 0.024) | angle < 40"))
```

>>>>

```{r eval=FALSE}
fwrite(data_copy, file = "data/data_errors.csv")
```

@@

```{r}
# get 90 and 95 percentile of speed and turning angle
sapply(data_copy[, c("in_speed", "angle")], function(z) {
  quantile(z, probs = c(0.1, 0.9, 0.95), na.rm = TRUE)
})
```

@@

```{r}
# filter the copy by the 95th percentile
data_filtered <- atl_filter_covariates(data_copy,
    filters = c("(in_speed < 0.025 & out_speed < 0.025) | angle < 35"))
```
